---
title: "Week 4 Workbook"
author: "Odelia"
date: "3/17/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Import data**

```{r}
library(dplyr)
library(magrittr)
library(devtools)
library(easystats)
library(lubridate)
library(forcats)
library(tidyverse)
nz_0 <- readr::read_csv2(url("https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nz/nz.csv"))
f<-c("None Of The Time",
     "A Little Of The Time",
     "Some Of The Time",
     "Most Of The Time",
     "All Of The Time")
nz <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE)
```

**Question 1: Using the nz dataset, make all the hours variables into integers**

```{r}
e <- as.integer(as.numeric(nz$Hours.Exercise))
i <- as.integer(as.numeric(nz$Hours.Internet))
w <- as.integer(as.numeric(nz$Hours.Work))
n <- as.integer(as.numeric(nz$Hours.News))
c <- as.integer(as.numeric(nz$HoursCharity))
```

**Question 2a: Create a new indicator that standardises the Pol.Orient variable, create a new indicator that centers the Pol.Orient variable, create a new indicator that centres the Age variable in decade-long units. Do this in a single piped workflow.**

```{r}
nz1 <- nz %>%
    select(Pol.Orient, Age)%>%
    mutate(Pol.O = scale(Pol.Orient, scale = TRUE, center  = TRUE), Pol.O2 = scale(Pol.Orient, scale = FALSE, center = TRUE), A1 = scale(Age, scale = FALSE, center = TRUE)/10)
```

**Question 2b: Select Hour.Exercise and filter Wave 2019**

```{r}
nz2 <- nz %>%
     select(Pol.Orient, Age, Hours.Exercise)%>%
     mutate(Pol.O = scale(Pol.Orient, scale = TRUE, center  = TRUE), Pol.O2 = scale(Pol.Orient, scale = FALSE, center = TRUE), A1 = scale(Age, scale = FALSE, center = TRUE)/10)%>%
filter(nz$Wave!=2019)
```

**Question 3: What are the maximum number of responses for a single day in 2018 and the maximum number of responses for a single day in 2019?**

library(kableExtra)
nz %>%
    select(date, Wave) %>%
    group_by(Wave, date) %>%
    summarise(n = n())%>%
    kbl(caption = "No. of responses per day") %>%
    kable_classic_2(c("striped", "hover"), full_width = TRUE)%>%
    collapse_rows()

Maximum number of responses for 2018: 121 on 2018-06-21

Maximum number of responses for 2019: 67 on 2019-12-03

**Question 4: How many days are there between the date with the highest number of responses and the date with the second highest number of responses? Bonus: Calculate difference between the number of responses on the highest response date and second highest response date.**

There is 1 day between the date with the highest number of responses (2018-06-21) and the date with the second highest number of responses (2018-06-22).

Difference between number of responses in the dates above:
121-104=17

**Question 5: Suppose you were born on Dec 25, 1995 at 5.02:22 am Calculate your age in months on March 20,2021, at 1:22:04pm. (Hint use the lubridate package. Look up the interval function).**

```{r}
int<-lubridate::interval(ymd_hms("1995-12-25 05:02:22"), ymd_hms("2021-03-20 13:22:04"))
time_length(int,"month")
```

My age in months will be 302.8338.

**Question 6: The Religion.Church variable contains responses to the question: “How many times each month do you attend church or religious service?” Create factor with the following three levels: 1.People who attend church 0 times per month, 2.People who attend church 1-3 times per month, 3.People who attend church 4 or more times per month. Make sure to re-level the factor so that the ordinal ranking moves from lowest to highest.**

nb. People who attended 0 times/month are coded as "Low", 1-3 times/month coded as "Moderate", and >=4 times/month coded as "High".

```{r}
R<-nz %>%
  dplyr::mutate(rc =  as.factor(ifelse(Religion.Church <= 0,"Low",ifelse(Religion.Church <= 3,  "Moderate", "High"))), rc=fct_relevel(rc,"Low","Moderate","High")) %>%
  group_by(rc) %>%
  count()
```

**Question 7: Using methods described in Lecture 4, create a table for average hours of sleep by month in the nz dataset. Graph the average hours of sleep by month including 95% confidence intervals. Briefly explain why some intervals are wider than others.**

I couldn't solve this after 3 whole days on it. Please teach me :')

**Question 8: Create a correlation graph for the items in the Kessler 6 scale. These are:-FeelHopeless, -FeelDepressed, -FeelRestless, -EverythingIsEffort, -FeelWorthless, -FeelNervous. What do you find most interesting about this plot? Explain.**

```{r}
c<-nz%>%
  select(FeelHopeless,FeelDepressed,FeelRestless,FeelWorthless,FeelNervous,EverythingIsEffort)%>%
  mutate_all(as.integer)%>%
  mutate(KESSLER6sum = as.factor(nz$KESSLER6sum))
library(correlation)
library(ggraph)
c1<-correlation(c, partial = FALSE, multilevel = TRUE)%>%
  plot()
c1
```

I find that the aesthetics of this plot to be the most interesting. The plot is visually a 2D plot but as I look as it, it depicts a 3D plot in my brain instead and it is very clear to see the strengths of the correlations between one another for every variable even when it is in actuality a 2D plot for as many as 5 variables. It is also able to show me negative correlations clearly with a different colour so I can easily tell positive and negative correlations apart.

**Question 9: Create a blank papaja report**

As attached.

**Question 10: Use the patchwork library to create a figure with two plots on top of each other. Use the tag_levels function to index each of the two plots. The graphs should describe some dimension of the truncated nz dataset.**

```{r}
c2<-c%>%
  correlation(partial = FALSE, multilevel = FALSE)%>%
  plot()
library(patchwork)
c1 / c2 + 
  plot_annotation(title = "Plot of multilevel (a) and single-level (b) correlation", tag_levels = 'a')
```
